Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-03-22 ms.tex
minor edit
right timeline for WISE mission phases

\begin{abstract} 
The Near Earth Object Wide-field Infrared Survey Explorer (NEOWISE)
Reactivation mission released data from its first full year of observations
in 2015. This data set includes $\sim$2.5 million exposures in each of W1 and
W2, effectively doubling the amount of WISE imaging available at 3.4$\mu$m and 
4.6$\mu$m relative to the AllWISE release. We have created the first ever 
full-sky set of coadds combining all publicly available W1 and W2 exposures 
from both the AllWISE and NEOWISE-Reactivation (NEOWISER) mission phases. We 
employ an adaptation of the unWISE image coaddition framework \citep{lang14}, 
which preserves the native WISE angular resolution and is optimized for forced 
photometry. By incorporating two additional scans of the entire sky, we not 
only improve the W1/W2 depths, but also largely eliminate time-dependent 
artifacts such as off-axis scattered moonlight. We anticipate that our new 
coadds will have a broad range of applications, including target selection for 
upcoming spectroscopic cosmology surveys, identification of distant/massive 
galaxy clusters, and discovery of high-redshift quasars. In particular, our 
full-depth AllWISE+NEOWISER coadds will be an important input for the Dark 
Energy Spectroscopic Instrument (DESI) selection of luminous red galaxy and 
quasar targets. Our full-depth W1/W2 coadds are already in use within the 
DECam Legacy Survey (DECaLS) and Mayall z-band Legacy Survey (MzLS) reduction 
pipelines. Much more work still remains in order to fully leverage NEOWISER 
imaging for astrophysical applications beyond the inner solar system.
\end{abstract}

@@

WISE launched in December 2009, and undertook a seven 
month, full-sky survey in all of W1-W4 from February 2010 through August
2010. In September 2010, the solid hydrogen cryogen used to cool the W3 and W4 
instrumentation was depleted, significantly reducing the quality of W3 
imaging and rendering W4 unusable. Nevertheless, WISE continued surveying 
the sky from September 2010 to February 2011 in W1 and W2, including 
a portion of the mission referred to as NEOWISE \citep{neowise}. In February 
2011 WISE was placed in hibernation. In October 2013, WISE was reactivated, and
recommenced surveying the sky in W1 and W2. This W1/W2 survey is referred to as 
NEOWISE-Reactivation (NEOWISER) and is expected to continue until 2017. The
first-year NEOWISER data products, including all single-exposure images,
were publicly released in March 2015. Importantly, the NEOWISER images are of 
very nearly the same high quality as those of the pre-hibernation WISE mission
\citep{neowiser}.

>>>>

\begin{abstract} 
The Near Earth Object Wide-field Infrared Survey Explorer (NEOWISE)
Reactivation mission released data from its first full year of observations
in 2015. This data set includes $\sim$2.5 million exposures in each of W1 and
W2, effectively doubling the amount of WISE imaging available at 3.4$\mu$m and 
4.6$\mu$m relative to the AllWISE release. We have created the first ever 
full-sky set of coadds combining all publicly available W1 and W2 exposures 
from both the AllWISE and NEOWISE-Reactivation (NEOWISER) mission phases. We 
employ an adaptation of the unWISE image coaddition framework \citep{lang14}, 
which preserves the native WISE angular resolution and is optimized for forced 
photometry. By incorporating two additional scans of the entire sky, we not 
only improve the W1/W2 depths, but also largely eliminate time-dependent 
artifacts such as off-axis scattered moonlight. We anticipate that our new 
coadds will have a broad range of applications, including target selection for 
upcoming spectroscopic cosmology surveys, identification of distant/massive 
galaxy clusters, and discovery of high-redshift quasars. In particular, our 
full-depth AllWISE+NEOWISER coadds will be an important input for the Dark 
Energy Spectroscopic Instrument (DESI) selection of luminous red galaxy and 
quasar targets. Our full-depth W1/W2 coadds are already in use within the 
DECam Legacy Survey (DECaLS) and Mayall z-band Legacy Survey (MzLS) reduction 
pipelines. Much more work still remains in order to fully leverage NEOWISER 
imaging for astrophysical applications beyond the solar system.
\end{abstract}

@@

WISE launched in December 2009, and undertook a seven 
month, full-sky survey in all of W1-W4 from early January 2010 until 
early August 2010. Due to the depletion of cryogen, W4 and W3 became unusable 
in early August 2010 and late September 2010, respectively. Nevertheless, WISE 
continued surveying the sky through January 2011 in W1 and W2, 
including a portion of the mission referred to as NEOWISE \citep{neowise}. In 
February 2011 WISE was placed in hibernation. In October 2013, WISE was 
reactivated, and recommenced surveying the sky in W1 and W2. This W1/W2 survey 
is referred to as NEOWISE-Reactivation (NEOWISER) and is expected to continue 
until 2017. The first-year NEOWISER data products, including all 
single-exposure images, were publicly released in March 2015. Importantly, the 
NEOWISER images are of very nearly the same high quality as those of the 
pre-hibernation WISE mission \citep{neowiser}.
